### 2016-03-15 paper/optical_flow.tex
yasu

\subsection{Swarm Fusion optical flow}

Fusion Move was first introduced by Lempitsky et al.~\cite{fusion_flow} to
solve the optical flow problem.
% Optical flow was the problem, in which the Fusion Move method was first
%introduced by Lempitsky et al.~\cite{viktor}.
We copy their problem setting and use images from the Middlebury optical
flow benchmark~\cite{middlebury_optical_flow}. We share similar proposal
generation schemes with Lempitsky et al~\cite{fusion_flow}
%instead of the HS algorithm, we
 with some modifications.~\footnote{First, we use more recent
   Farneback algorithm and change the level of pyramids from 1 to 5,
   then use either 3, 5 or 7 for parameter ``polyN''. Besides the
   clustering idea, we add three simple proposal generation schemes
   based on the current solution as suggested in
   \cite{fusion_flow}. In \textit{shift proposal}, the flow field in
   the current solution is shifted in either x or y directions for
   either 1, 2 or 3 pixels. In \textit{stagger proposal}, the flow
   field is shifted by a vector randomly drawn from a Gaussian
   distribution. In \textit{perturb proposal}, each flow value in the
   field is independently shifted by a vector randomly drawn from a
   Gaussian distribution. We choose schemes randomly when generating
   proposals.}

@@

\noindent
%The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
%are used to evaluate the effectiveness of our method.
The three swarm architectures in Fig.~\ref{fig:model} (SF-MF, SF-SS,
SF) have been evaluated against the competing methods. For SF-MF, each
thread repeats generating solution proposals ($\alpha=1, \beta=0$) for
four iterations and fuses with one solution from others ($\alpha=0,
\beta=1$) in one iteration. This pattern is repeated. For SF-SS, each
thread generates three solution proposals for fusion in each iteration
($\alpha=3$, $\beta=0$). For SF, we repeat the pattern of four
iterations with ($\alpha=3, \beta=0$) plus one iteration with ($\alpha=0,
\beta=3$).
%%
%Note that we have used the same set of proposal generation schemes as
%the competing methods.
We have used TRW-S for multi-way fusion and QPBO for binary fusion.
% , while our fusions are multi-way, for which we have used TRW-S.
%
% The full swarm fusion model (at the bottom right in
% Fig.~\ref{fig:model}) will be used to evaluate the effectiveness of our
% method. We will also try the other two Swarm fusion variants in
% Fig.~\ref{fig:model} with restrictions.
%
% 2 k-way 1 solution sharing. \chen{?}

>>>>

\subsection{Swarm Fusion optical flow}
Fusion Move was first introduced by Lempitsky et al.~\cite{fusion_flow} to
solve the optical flow problem.
% Optical flow was the problem, in which the Fusion Move method was first
%introduced by Lempitsky et al.~\cite{viktor}.
We copy their problem setting and use images from the Middlebury optical
flow benchmark~\cite{middlebury_optical_flow}. We share similar proposal
generation schemes with Lempitsky et al~\cite{fusion_flow}
%instead of the HS algorithm, we
 with some modifications.~\footnote{First, we use more recent
   Farneback algorithm and change the level of pyramids from 1 to 5,
   then use either 3, 5 or 7 for parameter ``polyN''. Besides the
   clustering idea, we add three simple proposal generation schemes
   based on the current solution as suggested in
   \cite{fusion_flow}. In \textit{shift proposal}, the flow field in
   the current solution is shifted in either x or y directions for
   either 1, 2 or 3 pixels. In \textit{stagger proposal}, the flow
   field is shifted by a vector randomly drawn from a Gaussian
   distribution. In \textit{perturb proposal}, each flow value in the
   field is independently shifted by a vector randomly drawn from a
   Gaussian distribution. We choose schemes randomly when generating
   proposals.}

@@

\noindent
%The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
%are used to evaluate the effectiveness of our method.
The three swarm architectures in Fig.~\ref{fig:model} (SF-MF, SF-SS, SF)
have been evaluated against the competing methods. For SF-MF, each
thread repeats generating solution proposals ($\alpha=1, \beta=0$) for
four iterations and fuses with one solution from others ($\alpha=0,
\beta=1$) in one iteration. This pattern is repeated. For SF-SS, each
thread generates three solution proposals for fusion in each iteration
($\alpha=3$, $\beta=0$). For SF, we repeat four iterations of
($\alpha=3, \beta=0$) and  one iteration of ($\alpha=0, \beta=3$).
%%
%Note that we have used the same set of proposal generation schemes as
%the competing methods.
We have used TRW-S for multi-way fusion and QPBO for binary fusion.
% , while our fusions are multi-way, for which we have used TRW-S.
%
% The full swarm fusion model (at the bottom right in
% Fig.~\ref{fig:model}) will be used to evaluate the effectiveness of our
% method. We will also try the other two Swarm fusion variants in
% Fig.~\ref{fig:model} with restrictions.
%
% 2 k-way 1 solution sharing. \chen{?}
